---
title: "Title Template"
author: "Samuel D. McQuillin, Ph.D. University of South Carolina"
twitter: "@samcq"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: ioslides_presentation
logo: logo.png
css: temp.css
widescreen: TRUE
---
<script src="https://ajax.googleapis.com/ajax/libs/jquery/1.12.2/jquery.min.js"></script>

<script>
    $(document).ready(function() {
    $('slide:not(.title-slide, .backdrop, .segue)').append('<footer></footer>');    
    $('footer').attr('label', 'SD McQuillin, 2016');

  })
</script>

<style>
  footer:after {
    font-size: 12pt;
    content: attr(label);
    position: absolute;
    margin-left: auto;
    margin-right: auto;
    left: 0;
    right: 0;
    text-align:center;
    bottom: 20px;
    line-height: 1.9;
    display: block;
  }
</style>


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

